MaxEnt: What is it good for?

### 2015-06-16 ms.tex
Fixed citation

We start with a {\it hypothesis space} of mutually exclusive and
exhaustive propositions $A_1$, $A_2$, ..., $A_N$. One and only one of these
propositions is true, but we don't know which. We model states of
uncertainty by probability distributions over the hypothesis space,
such as $\{p_i\}_{i=1}^N$ where $P(A_i) = p_i$ is the probability of $A_i$.
Of course all of the $p_i$ must be non-negative and their sum must be 1.
From this probability distribution, various probabilities can be derived
using the sum and product rules. For example, the probability of
$A_4$ {\bf or} $A_5$ is $p_4 + p_5$, and the probability of $A_5$ given
$A_5$ {\bf or} $A_6$ is $p_5/(p_5 + p_6)$. The rules of probability must
be obeyed if the rules for combining are to remain consistent
with the symmetries of logical {\bf and} and {\bf or} \citep{knuth_skilling}.

>>>>

We start with a {\it hypothesis space} of mutually exclusive and
exhaustive propositions $A_1$, $A_2$, ..., $A_N$. One and only one of these
propositions is true, but we don't know which. We model states of
uncertainty by probability distributions over the hypothesis space,
such as $\{p_i\}_{i=1}^N$ where $P(A_i) = p_i$ is the probability of $A_i$.
Of course all of the $p_i$ must be non-negative and their sum must be 1.
From this probability distribution, various probabilities can be derived
using the sum and product rules. For example, the probability of
$A_4$ {\bf or} $A_5$ is $p_4 + p_5$, and the probability of $A_5$ given
$A_5$ {\bf or} $A_6$ is $p_5/(p_5 + p_6)$. The rules of probability must
be obeyed if the rules for combining are to remain consistent
with the symmetries of logical {\bf and} and {\bf or}
\citep{2010arXiv1008.4831K}.
